Stack Safety as a Security Property

### 2020-07-07 main.tex
wbcf examples

\subsection{Attacker Model + Unsafe Variations}

@@

@@

\paragraph*{Bad write}

@@

\paragraph*{Bad read}

@@

\paragraph*{Control flow}

\leo{What should we do here? Overwrite our own ra and return?}

\paragraph*{Reusing call frames}

\leo{TODO}

@@

@@

@@

\definition{Well Bracketed Control Flow}
The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy {\em well
  bracketed control flow} with regard to those maps.

>>>>

\subsection{Attacker Model}

@@

\subsection{Unsafe Variations}

@@

\paragraph*{Bad Write}

@@

\paragraph*{Bad Read}

@@

\paragraph*{Bad Control Flow}

\[
5 : \jalr ~ r_4 ~ \rra ~ 0 
\]
If a jump instruction was added to {\tt main} with its target being
the middle of the code block of {\tt h}.

@@

For example, consider the unsafe substitution:
\[
5 : ~ \jalr ~ r_4 ~ \rra ~ 0
\]
This violates control separation as the instruction that causes a
function switch is not a valid call (or a return) according to the
call map.

@@

The same unsafe substitution violates entry integrity
\[
5 : ~ \jalr ~ r_4 ~ \rra ~ 0
\]
as its target (instruction 42) is not an established entry point for
{\tt h} according to the entry map.

\leo{Note something about not enforcing control flow integrity
  with allowing a call from {\tt main} to {\tt h}?}

@@

For example, if we added an instruction between 45 and 46:
\[
45.5: ~ \addi ~ \rra ~ r_0 ~ \negate 19
\]
This would cause the return from {\tt h} to go to instruction 8 and
return to {\tt main} instead of {\tt g}. While the instruction that
causes the return would still be a valid return (satisfying control
separation), the state after the return would not correspond to an
$\Unmatched$ return for {\tt g}'s call to {\tt h}, violating return
integrity.

\definition{Well Bracketed Control Flow}

The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy {\em well
  bracketed control flow} with regard to those maps.
